### 2019-11-06 thesis/txt/0-introduction.tex
add 3 plots, describe new plots in results, discuss results cleaner

There are different techniques used to retrieve information from CI build logs. Beller et al. use regular expressions to analyze the failure reasons of Ruby and Java Maven build logs from TravisCI~\cite{beller2017oops}.
In general, such regular expressions are developed by looking at a few exemplary build logs and updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
Vassallo et al. wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
Recently, Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.

@@

\plan{results and conclusions of my work}
Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that PROSE is suitable for retrieval tasks requiring a high precision, ... . Retrieving information by using text similarity of examples is suitable when ... . Simple keyword search is suitable ... .

@@

This thesis first presents an overview of the related research, spanning from CI research, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
Next, chapter \ref{sec:models} presents our models for information retrieval techniques, use case scenarios for such techniques and retrievable information from CI build logs. It also introduces the three techniques, we focus on during our research evaluation.
Chapter \ref{sec:data-set} describes the creation of our \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs and the labeling as well as the validation process.
Following, Chapter \ref{sec:implementation} our implementation of the three chosen information retrieval techniques and the usage of our unified information retrieval tool.
This tool is also used for the evaluation study of our models described in Chapter \ref{sec:study}. There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity, and keyword search.
Lastly, we conclude and give an overview of further research opportunities in Chapter \ref{sec:conclusion}.
\end{document}

>>>>

There are different techniques used to retrieve information from CI build logs. Beller et al.\ use regular expressions to analyze the failure reasons of Ruby and Java Maven build logs from TravisCI~\cite{beller2017oops}.
In general, such regular expressions are developed by looking at a few exemplary build logs and updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
Vassallo et al.\ wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
Recently, Amar et al.\ greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.

@@

\plan{results and conclusions of my work}
Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that PROSE is suitable for retrieval tasks requiring a high precision,. Retrieving information by using text similarity of examples is suitable when. Simple keyword search is suitable.

@@

This thesis first presents an overview of the related research, spanning from CI research, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
Next, chapter~\ref{sec:models} presents our models for information retrieval techniques, use case scenarios for such techniques and retrievable information from CI build logs. It also introduces the three techniques, we focus on during our research evaluation.
Chapter~\ref{sec:data-set} describes the creation of our \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs and the labeling as well as the validation process.
Following, Chapter~\ref{sec:implementation} our implementation of the three chosen information retrieval techniques and the usage of our unified information retrieval tool.
This tool is also used for the evaluation study of our models described in Chapter~\ref{sec:study}. There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity, and keyword search.
Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.
\end{document}

### 2019-11-06 thesis/txt/1-related-work.tex
add 3 plots, describe new plots in results, discuss results cleaner

The structure of build logs
\begin{itemize}
  \item is \textbf{implicit}.
  We do not have access to explicit structuring elements or an explicit structure description.
  Computation is required to infer the present structure.
  \item is \textbf{irregular}.
  Changes in the build process or execution environment might change the structure of a build log without notice.
  We observed this in the logs we collected for the \emph{Failing Build Log Data Set}, where for the same repository and build configuration some logs had double new line characters without any noticeable explanation.
  You can see an example of this in Figure \ref{fig:log-4} and Figure \ref{fig:log-5}.
  \item is \textbf{partial}. Some parts are highly structured by e.g.\ structure indicating special characters and others are unstructured, e.g.\ natural language text in error messages.
  \item can be described with an \textbf{a-posteriori data guide} rather than an a-priori schema.
  There is no fixed specification on how build tools have to structure their output.
  We afterwards extract structuring patterns in the produced output.
  \item has a \textbf{rapidly evolving} schema.
  Modifications in the build configuration might change the tools involved in the build and therefore the composition of the build log.
  Previous work indicates that some projects change their CI configuration often~\cite{hilton2016usage} and software tools adopt their log messages over time~\cite{yuan2012characterizing}.
\end{itemize}

@@

\section{Program Synthesis by Example}
\label{sec:rw-prose}
\plan{extend, 1 page}
\todo{how much can/should we explain here? possibly big parts are already explained in related work: vsa, divied and coquer, witness functions, enumeration and ranking (prose theory paper), flash extract specifics like what functions they have (absolute pos, pre/post regex), rankings specific to ci biulg logs?}
\review{
Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework. It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples. Users can extract multiple fields and structure them with hierarchy and sequence. FlashExtract eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.

We are applying FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information retrieval.
}
\mention{prose theory paper \cite{polozov2015flashmeta:}}
\mention{\cite{rolim2017learning}}

>>>>

The structure of build logs
\begin{itemize}
  \item is \textbf{implicit}.
  We do not have access to explicit structuring elements or an explicit structure description.
  Computation is required to infer the present structure.
  \item is \textbf{irregular}.
  Changes in the build process or execution environment might change the structure of a build log without notice.
  We observed this in the logs we collected for the \emph{Failing Build Log Data Set}, where for the same repository and build configuration some logs had double new line characters without any noticeable explanation.
  You can see an example of this in Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5}.
  \item is \textbf{partial}. Some parts are highly structured by e.g.\ structure indicating special characters and others are unstructured, e.g.\ natural language text in error messages.
  \item can be described with an \textbf{a-posteriori data guide} rather than an a-priori schema.
  There is no fixed specification on how build tools have to structure their output.
  We afterwards extract structuring patterns in the produced output.
  \item has a \textbf{rapidly evolving} schema.
  Modifications in the build configuration might change the tools involved in the build and therefore the composition of the build log.
  Previous work indicates that some projects change their CI configuration often~\cite{hilton2016usage} and software tools adopt their log messages over time~\cite{yuan2012characterizing}.
\end{itemize}

@@

\section{Program Synthesis by Example}
\label{sec:rw-prose}
\plan{extend, 1 page}
\todo{how much can/should we explain here? possibly big parts are already explained in related work: vsa, divied and coquer, witness functions, enumeration and ranking (prose theory paper), flash extract specifics like what functions they have (absolute pos, pre/post regex), rankings specific to ci biulg logs?}
\review{Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework. It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples. Users can extract multiple fields and structure them with hierarchy and sequence. FlashExtract eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.

We are applying FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information retrieval.
}
\mention{prose theory paper~\cite{polozov2015flashmeta:}}
\mention{\cite{rolim2017learning}}

### 2019-11-06 thesis/txt/2-models.tex
incorporate second kw 44 sturcture feedback
restart study chapter
add 3 plots, describe new plots in results, discuss results cleaner

Software tools involved in the build write out log messages to the console.
They communicate progress updates, error and warning messages to the user~\cite{yuan2012characterizing}.
We refer to to the sum of this output as build log.
The structure of their output is chosen by every tool themselves.
Many have implicit or explicit structuring rules, some adhere to predefined standards like RSpec or PHPUnit~\cite{phpunit2019logging,rspec2019format}.
Figure \ref{fig:tool-log-contribution} shows how different tools contribute to the whole build log.

@@

When analyzing build logs we might not have access to the exact build configuration, describing which tools are used in which order, or might not have access to a useable definition of the output structure of a specific tool.
As the structure of a build log is not known to us, we describe build logs as semi-structured. Section \ref{sec:rw-semi-structured-data} describes different properties of semi-structured data.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/build-log-information.pdf}
	\caption{Information retrievable from build logs}
	\label{fig:build-log-information}
\end{figure}
\section{Information Chunks in Build Logs}
\label{sec:bli}
Continuous integration build logs contain a huge amount of information about the stages in the CI build they correspond to.
In this section, we present a model, which more precisely describes our notion of a information retrievable from a CI build log.
Figure \ref{fig:build-log-information} shows the model.

@@

Each BLII for us has a \emph{textual representation} within the build log.
This textual representation is always a substring of the log text.
BuildLogInformations can be hierarchically ordered by their textual representations containing each other.
As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section \ref{sec:rw-semi-structured-data}, the model only presents hierarchical ordering or containment for BuildLogInformations whose structure we definitely know.
Most build log information types can appear in various hierarchical arrangements and therefore not contained in any other type in the model.

@@

	      A TravisPhase always contains:
	      \begin{itemize}
		      \item \textbf{TravisPhaseName} The string Travis CI uses to identify the phase within start and end statements.
		      \item \textbf{TravisPhaseOutput} The output generated during the build step. The textual representation of the \texttt{Build Step Output} Instantiation is the substring between the start and end statements.
	      \end{itemize}
	      You can see an example of a TravisPhase and its components within a build log in Figure \ref{fig:log-1}.

	\item
	\item \textbf{TravisTiming} Travis can measure the time of specified sections of the build process.
	      Timing information can be useful to retrieve when you want to automatically monitor the performance of your build.
	      You can see an example of a Travis Build Step and its components within a build log in Figure \ref{fig:log-1}.
	      %It represents those by \lstinline{travis_time:start:<timing section id>} and \\ \lstinline{travis_time:end:<timing section id>:start=<start time>,finish=<finish time>,duration=<duration>}

	\item \textbf{TravisWorker} Travis CI mentions for each build which machine is executing it.
	      Retrieving this information from multiple build logs could for example help visualize the impact of the build server assignment algorithm.
	      The TravisWorker is a good example to show that the same BLI can have different textual representations in different build logs.
	      You can see examples of TravisWorker instantiations in Figure \ref{fig:log-0} and Figure \ref{fig:log-2}.

	\item \textbf{TravisSystemInfo} At the beginning of each log Travis CI describes the tech stack of the server executing the build.
	      The system info could be retrieved from both failing and successful logs and compared to identify if a failure is possibly based on the execution environment.
	      You can see an example of a TravisSystemInfo instantiation within a build log in Figure \ref{fig:log-0}.

	\item \textbf{TriggeringCommand} Travis CI logs the commands it uses to call certain tools.
	      These come from the \texttt{travis.yml} configuring the build.
	      Retrieving this information from the log could, for example, be useful when reverse engineering the build configuration.
	      You can see an example of a TriggeringCommand instantiation within a build log in Figure \ref{fig:log-3}.

	\item \textbf{ExitCode} Travis CI prints all exit codes of commands.
	      This information could be used to fill an overview of the build steps and why they failed.
	      You can see an example of an ExitCode instantiation within a build log in Figure \ref{fig:log-3}.

	\item \textbf{ErrorMessage} Various tools involved in the build process might output messages of errors that occurred during their execution.
	      Retrieving these and showing them to developers could help them understand quicker why the build failed.
	      You can see an example of and ErrorMessage instantiation within a build log in Figure \ref{fig:log-3}.

	\item \textbf{WarningMessage} In addition to errors, tools also print warning messages.
	      These could be collected, counted and presented to developers, encouraging them to resolve them to improve their software.
	      You can see examples of WarningMessage instantiations within build logs in Figure \ref{fig:log-4} and Figure \ref{fig:log-5}.

@@

% \section{Information Retrieval Tasks}
% \label{sec:blir-tasks}
% \plan{what do we need here?, come up with model if we keep this, 1 page text max.}
% Previous sections gave various examples of situations where a developer or a researcher wants to retrieve information from a build log.
% The goal of this work is to clarify which BLIRT is suited for their specific task.
% In this section we structure we present different important characteristics of such an IR task.
% You can see the model in Figure \ref{fig:model-ir-task}

@@

\emph{Programming by Example (PBE)} is a technique where programs are synthesized according to in and output examples provided by the user.
It enables users to create programs without requiring programming knowledge~\cite{mayer2015user}.
Applied to the task of text extraction through regular expressions it relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
We chose to investigate the applicability of generating regular expression programs by example to extracting information from build logs.
In this work, we refer to our interpretation of this technique as \emph{PBE}.
In the following we will explain the concept of how we apply PBE to information retrieval from CI build logs, the concrete implementation is described in \ref{sec:impl-pbe}.
Figure \ref{fig:prose-explanation} shows the instantiation of the BLIRT model for PBE.

\paragraph{Method}
In/Output examples (I/O examples) are the main driver of Programming by Example.
When extracting information from build logs the \emph{input} is always a whole build log, i.e. the whole text of the build log file without any preprocessing.
In the implementation, we had to apply a few text replacements as described in \ref{sec:impl-preprocessing}.
The \emph{output} is always a substring of the log file text, representing the substring that should be extracted by the synthesized program when given the corresponding input file.
One or multiple I/O examples are needed as configuration for PBE, they are used to define substring of a log should be extracted.
Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm.
Both are described in Section \ref{sec:rw-prose}.
%For execution PBE takes a build file as input and returns a substring of the build file content.

@@

Text Similarity approaches are more and more used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
One common and simple technique the Vector Space Model~\cite{schutze2008introduction}.
We investigate when it is a suitable technique to retrieve information from build logs.
In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs (TS), the concrete implementation is described in \ref{sec:impl-ts}.
Figure \ref{fig:text-similarity-explanation} shows the instantiation of the BLIRT model for TS.

@@

When we are looking for a specific piece of information within a great amount of unstructured information, a first ad-hoc approach is to search for keywords in the text we assume to be near the information we are looking for.
This was one of the most common approaches we took when searching for the build failure reason within a log when creating our data set.
As this is a technique readily available in many tools developers use to view build logs, we want to study when such a simple search for keywords is recommendable for retrieving information from CI build logs.
In the following we will explain how we use simple keyword search to retrieve information from CI build logs (SKWS), the concrete implementation is described in \ref{sec:impl-skws}.
Figure \ref{fig:keyword-search-explanation} shows the instantiation of the BLIRT model for SKWS.

@@

\subsection{Random Line Retrieval (RLR)}

@@

\paragraph{Log Diff}
Amar et al. used a technique based on line diffs to retrieve relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section \ref{sec:rw-bl-analysis}.
Figure \ref{fig:diff-technique-model} shows how this technique would be in our BLIRT model.
\paragraph{Random Line Retrieval}
In our evaluation we want to compare against a basic deadline of randomly extracted lines.
The random line retrieval technique (RLR) averages the number of lines in the outputs of the configuring examples and extracts this many lines randomly from the build log.

>>>>

Software tools involved in the build write out log messages to the console.
They communicate progress updates, error and warning messages to the user~\cite{yuan2012characterizing}.
We refer to to the sum of this output as build log.
The structure of their output is chosen by every tool themselves.
Many have implicit or explicit structuring rules, some adhere to predefined standards like RSpec or PHPUnit~\cite{phpunit2019logging,rspec2019format}.
Figure~\ref{fig:tool-log-contribution} shows how different tools contribute to the whole build log.

@@

When analyzing build logs we might not have access to the exact build configuration, describing which tools are used in which order, or might not have access to a useable definition of the output structure of a specific tool.
As the structure of a build log is not known to us, we describe build logs as semi-structured. Section~\ref{sec:rw-semi-structured-data} describes different properties of semi-structured data.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/build-log-information.pdf}
	\caption{Information retrievable from build logs}
	\label{fig:build-log-information}
\end{figure}
\section{Information Chunks in Build Logs}
\label{sec:bli}
Continuous integration build logs contain a huge amount of information about the stages in the CI build they correspond to.
In this section, we present a model, which more precisely describes our notion of a information retrievable from a CI build log.
Figure~\ref{fig:build-log-information} shows the model.

@@

Each BLII for us has a \emph{textual representation} within the build log.
This textual representation is always a substring of the log text.
BuildLogInformations can be hierarchically ordered by their textual representations containing each other.
As this is an ad-hoc and a-posteriori structuring schema, as we describe in Section~\ref{sec:rw-semi-structured-data}, the model only presents hierarchical ordering or containment for BuildLogInformations whose structure we definitely know.
Most build log information types can appear in various hierarchical arrangements and therefore not contained in any other type in the model.

@@

	      A TravisPhase always contains:
	      \begin{itemize}
		      \item \textbf{TravisPhaseName} The string Travis CI uses to identify the phase within start and end statements.
		      \item \textbf{TravisPhaseOutput} The output generated during the build step. The textual representation of the \texttt{Build Step Output} Instantiation is the substring between the start and end statements.
	      \end{itemize}
	      You can see an example of a TravisPhase and its components within a build log in Figure~\ref{fig:log-1}.

	\item
	\item \textbf{TravisTiming} Travis can measure the time of specified sections of the build process.
	      Timing information can be useful to retrieve when you want to automatically monitor the performance of your build.
	      You can see an example of a Travis Build Step and its components within a build log in Figure~\ref{fig:log-1}.
	      %It represents those by \lstinline{travis_time:start:<timing section id>} and \\ \lstinline{travis_time:end:<timing section id>:start=<start time>,finish=<finish time>,duration=<duration>}

	\item \textbf{TravisWorker} Travis CI mentions for each build which machine is executing it.
	      Retrieving this information from multiple build logs could for example help visualize the impact of the build server assignment algorithm.
	      The TravisWorker is a good example to show that the same BLI can have different textual representations in different build logs.
	      You can see examples of TravisWorker instantiations in Figure~\ref{fig:log-0} and Figure~\ref{fig:log-2}.

	\item \textbf{TravisSystemInfo} At the beginning of each log Travis CI describes the tech stack of the server executing the build.
	      The system info could be retrieved from both failing and successful logs and compared to identify if a failure is possibly based on the execution environment.
	      You can see an example of a TravisSystemInfo instantiation within a build log in Figure~\ref{fig:log-0}.

	\item \textbf{TriggeringCommand} Travis CI logs the commands it uses to call certain tools.
	      These come from the \texttt{travis.yml} configuring the build.
	      Retrieving this information from the log could, for example, be useful when reverse engineering the build configuration.
	      You can see an example of a TriggeringCommand instantiation within a build log in Figure~\ref{fig:log-3}.

	\item \textbf{ExitCode} Travis CI prints all exit codes of commands.
	      This information could be used to fill an overview of the build steps and why they failed.
	      You can see an example of an ExitCode instantiation within a build log in Figure~\ref{fig:log-3}.

	\item \textbf{ErrorMessage} Various tools involved in the build process might output messages of errors that occurred during their execution.
	      Retrieving these and showing them to developers could help them understand quicker why the build failed.
	      You can see an example of and ErrorMessage instantiation within a build log in Figure~\ref{fig:log-3}.

	\item \textbf{WarningMessage} In addition to errors, tools also print warning messages.
	      These could be collected, counted and presented to developers, encouraging them to resolve them to improve their software.
	      You can see examples of WarningMessage instantiations within build logs in Figure~\ref{fig:log-4} and Figure~\ref{fig:log-5}.

@@

% \section{Information Retrieval Tasks}
% \label{sec:blir-tasks}
% \plan{what do we need here?, come up with model if we keep this, 1 page text max.}
% Previous sections gave various examples of situations where a developer or a researcher wants to retrieve information from a build log.
% The goal of this work is to clarify which BLIRT is suited for their specific task.
% In this section we structure we present different important characteristics of such an IR task.
% You can see the model in Figure~\ref{fig:model-ir-task}

@@

\emph{Programming by Example (PBE)} is a technique where programs are synthesized according to in and output examples provided by the user.
It enables users to create programs without requiring programming knowledge~\cite{mayer2015user}.
Applied to the task of text extraction through regular expressions it relieves the developer from having to understand the whole document structure to solve a single extraction task~\cite{le2014flashextract:}.
We chose to investigate the applicability of generating regular expression programs by example to extracting information from build logs.
In this work, we refer to our interpretation of this technique as \emph{PBE}.
In the following we will explain the concept of how we apply PBE to information retrieval from CI build logs, the concrete implementation is described in~\ref{sec:impl-pbe}.
Figure~\ref{fig:prose-explanation} shows the instantiation of the BLIRT model for PBE.

\paragraph{Method}
In/Output examples (I/O examples) are the main driver of Programming by Example.
When extracting information from build logs the \emph{input} is always a whole build log, i.e. the whole text of the build log file without any preprocessing.
In the implementation, we had to apply a few text replacements as described in~\ref{sec:impl-preprocessing}.
The \emph{output} is always a substring of the log file text, representing the substring that should be extracted by the synthesized program when given the corresponding input file.
One or multiple I/O examples are needed as configuration for PBE, they are used to define substring of a log should be extracted.
Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm.
Both are described in Section~\ref{sec:rw-prose}.
%For execution PBE takes a build file as input and returns a substring of the build file content.

@@

Text Similarity approaches are more and more used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
One common and simple technique the Vector Space Model~\cite{schutze2008introduction}.
We investigate when it is a suitable technique to retrieve information from build logs.
In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs (TS), the concrete implementation is described in~\ref{sec:impl-ts}.
Figure~\ref{fig:text-similarity-explanation} shows the instantiation of the BLIRT model for TS.

@@

When we are looking for a specific piece of information within a great amount of unstructured information, a first ad-hoc approach is to search for keywords in the text we assume to be near the information we are looking for.
This was one of the most common approaches we took when searching for the build failure reason within a log when creating our data set.
As this is a technique readily available in many tools developers use to view build logs, we want to study when such a simple search for keywords is recommendable for retrieving information from CI build logs.
In the following we will explain how we use simple keyword search to retrieve information from CI build logs (SKWS), the concrete implementation is described in~\ref{sec:impl-skws}.
Figure~\ref{fig:keyword-search-explanation} shows the instantiation of the BLIRT model for SKWS.

@@

@@

\paragraph{Log Diff}
Amar et al. used a technique based on line diffs to retrieve relevant lines from a failed build log~\cite{amar2019mining}, as we describe in more detail in Section~\ref{sec:rw-bl-analysis}.
Figure~\ref{fig:diff-technique-model} shows how this technique would be in our BLIRT model.
\paragraph{Random Line Retrieval (RLR)}
In our evaluation we want to compare against a basic deadline of randomly extracted lines.
The random line retrieval technique (RLR) averages the number of lines in the outputs of the configuring examples and extracts this many lines randomly from the build log.

### 2019-11-06 thesis/txt/3-data-set.tex
incorporate second kw 44 sturcture feedback
add 3 plots, describe new plots in results, discuss results cleaner

\section{Data Structure}
For our study, described in Chapter \ref{sec:study}, we want to investigate the retrieval capabilities of three techniques. Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}. Furthermore, Keyword search is not configured by such in/output, but search keywords surrounding the desired output. Finally, this section describes our notion of structural categories, which we use to quantify our assumptions on the needed uniformness of in/output examples.

@@

\section{Threats to Validity}
\bp{some errors are not shown inside the log: we always choose an extraction, if we did not see the actual reason for the error reported, we chose the part stating that an error occured / the build failed

@@

end all the points with: we tried to remedy this by (e.g.\ validations)
}

\section{Validation}
We vaildated our collected labels in two different ways. We did a second pass of labeling the build failure reason, keywords and categoies on a subset of the data and compared the results to calculate the inter-rater reliability using cohens kappa. In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set and asked them whether our retrieval of the log part describing the reason the build failed was correct. In the following we describe the results of those two validation studies.

@@

The person who probably knows best why a build failed is the one committing the changes which triggered the build.
If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
In this section we describe how we validate the extractions of the build failure reason the \emph{Failing Build Log Data Set} describes.
\subsubsection{Method}
Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.Figure \ref{fig:dev-mail} shows one of the mails sent out.
The email included links to the corresponding commits, build overview and log file.
We asked the receivers to fill out a short survey in case our extraction was not correct.
Look at Figure \ref{fig:dev-survey} to get an impression of the survey.
In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines in order to keep the mail readable.

@@

\subsubsection{Results}
In total we sent out mails to 246 developers, asking about 3.2 build logs on average.
32 of these mails could not be delivered, e.g. because they were addressed at noreply mail addresses.
These 32 mails related to 68 of the build logs.
We received answers from 61 developers, responding about 144 build logs.
The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure \ref{fig:mails-answers-received-mails} and Figure \ref{fig: mails-answers-received-builds}.

Of the 144 answers, 132 said our extraction was correct.
26 answered either "close, but not quite correct" or "no, the build failed for another reason".
We manually inspected these negative answers and found that extractions were correct after all.
This yields 12 log extractions in our example set that were not correct, shown in Figure \ref{fig:mails-extraction-correct}.

>>>>

\section{Data Structure}
For our study, described in Chapter~\ref{sec:study}, we want to investigate the retrieval capabilities of three techniques. Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}. Furthermore, Keyword search is not configured by such in/output, but search keywords surrounding the desired output. Finally, this section describes our notion of structural categories, which we use to quantify our assumptions on the needed uniformness of in/output examples.

@@

\section{Validation}
\bp{some errors are not shown inside the log: we always choose an extraction, if we did not see the actual reason for the error reported, we chose the part stating that an error occured / the build failed

@@

end all the points with: we tried to remedy this by (e.g.\ validations)
}
We vaildated our collected labels in two different ways. We did a second pass of labeling the build failure reason, keywords and categoies on a subset of the data and compared the results to calculate the inter-rater reliability using cohens kappa. In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set and asked them whether our retrieval of the log part describing the reason the build failed was correct. In the following we describe the results of those two validation studies.

@@

The person who probably knows best why a build failed is the one committing the changes which triggered the build.
If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
In this section we describe how we validate the extractions of the build failure reason the \emph{Failing Build Log Data Set} describes.
\subsubsection{Method}
Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.Figure~\ref{fig:dev-mail} shows one of the mails sent out.
The email included links to the corresponding commits, build overview and log file.
We asked the receivers to fill out a short survey in case our extraction was not correct.
Look at Figure~\ref{fig:dev-survey} to get an impression of the survey.
In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines in order to keep the mail readable.

@@

\subsubsection{Results}
In total we sent out mails to 246 developers, asking about 3.2 build logs on average.
32 of these mails could not be delivered, e.g. because they were addressed at noreply mail addresses.
These 32 mails related to 68 of the build logs.
We received answers from 61 developers, responding about 144 build logs.
The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure~\ref{fig:mails-answers-received-mails} and Figure~\ref{fig: mails-answers-received-builds}.

Of the 144 answers, 132 said our extraction was correct.
26 answered either "close, but not quite correct" or "no, the build failed for another reason".
We manually inspected these negative answers and found that extractions were correct after all.
This yields 12 log extractions in our example set that were not correct, shown in Figure~\ref{fig:mails-extraction-correct}.
